---
title: "Examples with {flextable}"
date: "`r format(Sys.time(), '%B %d, %Y')`"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, 
    output_dir = here::here("outputs"))
     })
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(palmerpenguins)
library(tidyverse)
library(flextable)
library(gtsummary)

data(penguins)

penguins <- penguins %>%
  bstfun::use_varnames_as_labels()

```

# Print a Plain Dataframe

```{r}
df <- penguins %>% 
  head(n =10)

df %>% flextable()

```


# {gtsummary} Example: Default Print Engine

Example where we don't specify print engine:

```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels()
```

# {gtsummary} Example: Specify Print Engine

```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_flex_table()
```

# {gtsummary} Example: With Compact Theme

```{r}
theme_gtsummary_compact()

penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_flex_table()

reset_gtsummary_theme()
```

# {gtsummary} Example: Add Title

```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels()  %>%
  as_flex_table() %>%
  add_header_row(values = "Title", colwidths = 2)

```

# {gtsummary} Example: Highlight Specific Values

```{r}
x <- penguins %>% 
  tbl_summary(by = species) %>%
  add_p() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_flex_table() %>%
  add_header_row(values = "Title", colwidths = 5)

# To inspect internals of gt object you can do:
# x$body$dataset

x$body$dataset <- x$body$dataset %>%
  mutate(new_cond = parse_number(stat_1)) 

x %>%
  flextable::bg(
    i = .$body$dataset$new_cond >= 50,
    j = "label",
    bg = "purple"
  ) %>%
  flextable::bg(
    i = .$body$dataset$p.value <= 0.05,
#    j = "label",
    bg = "red"
  )


```

# {gtsummary} Example: Merged Tables with Spanning Headers

```{r}
sum <- penguins %>%
  select(species, island, sex) %>%
  tbl_summary(by = species) %>%
  add_p()


reg <- glm(species ~ island + sex,
           family = binomial(), data = penguins) %>%
  tbl_regression(exponentiate = TRUE)

reg2 <- penguins %>%
  # species limited to certain islands
  select(-island) %>%
  tbl_uvregression(
  method = glm,
  y = species, 
  exponentiate = TRUE, 
  method.args = list(family = binomial())
)

x <- tbl_merge(list(sum, reg, reg2),
          tab_spanner = 
            c("**Summary Statistics**", "**Univariate***", 
              "**Multivariate***")) %>% 
  
  as_flex_table() 

# another spanner

x
```

# Add Footnotes 

Note: need to specify `part = header` to get in header

```{r}

x <- penguins %>% 
  head(n = 10) %>%
  flextable() 

x %>%
  footnote(.,
           i = 1,
           j = "island",
            part = "header",
           value = as_paragraph("Custom Footnote"))

```

# Saving Quickly 

```{r}
save_as_docx(x, path = here::here("outputs",     
                             "flextable-quick-table.docx"), pr_section = NULL)


#save_as_html()
#save_as_image()
```

