---
title: "Examples with {huxtable}"
date: "`r format(Sys.time(), '%B %d, %Y')`"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, 
    output_dir = here::here("outputs"))
     })
output:
  word_document
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(palmerpenguins)
library(tidyverse)
library(huxtable)
library(gtsummary)
library(labelled)

data(penguins)

penguins <- penguins %>%
  bstfun::use_varnames_as_labels()

```

# Print a plain dataframe 

```{r }
df <- penguins %>% 
  head(n =10)

df %>% huxtable()

```

# {gtsummary} Example: Default Print Engine

Example where we don't specify print engine:

```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels()
```

# {gtsummary} Example: Specify Print Engine

```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_hux_table()
```

# {gtsummary} Example: With Compact Theme

```{r}
theme_gtsummary_compact()

penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_hux_table()

reset_gtsummary_theme()
```


# {gtsummary} Example: Add Title


```{r}
penguins %>% 
  tbl_summary() %>%
  bold_labels() %>%
  italicize_levels()  %>%
  as_hux_table() %>%
  set_caption("Title") 

```

# {gtsummary} Example: Highlight Specific Values

```{r}
x <- penguins %>% 
  tbl_summary(by = species) %>%
  add_p() %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_hux_table() 

x <- x %>%
  mutate(new_cond = parse_number(stat_1)) %>%
  mutate(p_val_numeric = parse_number(p.value))

x %>%
  set_background_color(
    row = .$new_cond >= 50,
    col = "stat_1",
    value = "purple") %>%
  
  set_background_color(
    row = .$p_val_numeric <=  0.05,
    value = "red") %>%
  
  # have to de-select new column made for calculating
  select(-c(new_cond, p_val_numeric))
```

# {gtsummary} Example: Merged Tables with Spanning Headers

```{r}
sum <- penguins %>%
  select(species, island, sex) %>%
  tbl_summary(by = species) %>%
  add_p()


reg <- glm(species ~ island + sex,
           family = binomial(), data = penguins) %>%
  tbl_regression(exponentiate = TRUE)

reg2 <- penguins %>%
  # species limited to certain islands
  select(-island) %>%
  tbl_uvregression(
  method = glm,
  y = species, 
  exponentiate = TRUE, 
  method.args = list(family = binomial())
)

x <- tbl_merge(list(sum, reg, reg2),
          tab_spanner = 
            c("**Summary Statistics**", "**Univariate***", 
              "**Multivariate***")) %>% 
  
  as_hux_table() 

# another spanner

x
```

# Add Footnotes 

Couldn't specify position of footnote 

```{r}
x <- penguins %>% 
  head(n = 10) %>%
  hux() 

x %>%
  add_footnote(.,
               text = "Custom Footnote")


```


# Saving Quickly 

print objects to a PDF, TeX, HTML, Microsoft Office or RTF

```{r, eval = FALSE}
huxtable::quick_pdf(x,
                     here::here("outputs",
                                "hux-quick-table.pdf"))


#huxtable::quick_latex()
#huxtable::quick_pdf()
#huxtable::quick_docx()


```



